Sumbission Steps

### 2020-10-01 code/03-submission-steps.Rmd
small updates

---
title: "Sumbission Steps"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

@@

    ```{r}
    # Individual files to delete
    file.remove("../data/bullet-explain.rds")
    file.remove("../data/bullet-lime.rds")
    file.remove("../data/bullet-rf.rds")
    file.remove("../data/bullet-test.csv")
    file.remove("../data/bullet-test.csv.zip")
    file.remove("../data/bullet-train.csv")
    file.remove("../data/bullet-train.csv.zip")
    file.remove("../data/example-signatures.csv")
    file.remove("../data/example-signatures.csv.zip")
    file.remove("../data/sine-lime-explain.rds")
    file.remove("../figure-static/figure-08-1.eps")
    file.remove("../figure-static/figure-08-1.png.zip")
    file.remove("../figure-static/figure-10-1.eps")
    file.remove("../figure-static/figure-10-1.png")

@@

2. Manually run the code in `code/01-raw-file-compression.Rmd` to compress the raw versions of the data files and static figure. Also, knit the file to make sure the html version is up to date.

3. Manually run the code in `code/02-data-preparation.Rmd` to create the versions of the data to be used in the manuscript and submitted with the manuscript. Also, knit the file to make sure the html version is up to date.

@@

    # Create a vector with code and data files to be included for submission 
    data_files <-
      c(
        "../readme.txt",
        "../data/bullet-test.csv.zip",
        "../data/bullet-train.csv.zip",
        "../data/example-signatures.csv.zip"
      )

@@

7. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).

@@

>>>>

---
title: "Sumbission Steps"
author: "Katherine Goode"
date: "<br>`r format(Sys.time(), '%B %d, %Y')`"
output: rmarkdown::github_document
---

@@

    ```{r}
    # Individual files to delete
    file.remove("../data/bullet-explain.rds")
    file.remove("../data/bullet-lime.rds")
    file.remove("../data/bullet-rf.rds")
    file.remove("../data/bullet-test.csv")
    file.remove("../data/bullet-test.csv.zip")
    file.remove("../data/bullet-train.csv")
    file.remove("../data/bullet-train.csv.zip")
    file.remove("../data/example-signatures.csv")
    file.remove("../data/example-signatures.csv.zip")
    file.remove("../data/sine-lime-explain.rds")
    file.remove("../data/raw/h224-set1-features.rds")
    file.remove("../data/raw/h224-set1-features.rds.zip")
    file.remove("../data/raw/h224-set11-features.rds")
    file.remove("../data/raw/h224-set11-features.rds.zip")
    file.remove("../data/raw/CCFs_withlands.csv")
    file.remove("../data/raw/CCFs_withlands.csv.zip")
    file.remove("../data/raw/signatures.rds")
    file.remove("../data/raw/signatures.rds.zip")
    file.remove("../figure-static/figure-08-1.eps")
    file.remove("../figure-static/figure-08-1.png.zip")
    file.remove("../figure-static/figure-10-1.eps")
    file.remove("../figure-static/figure-10-1.png")

@@

2. Manually run the code in `code/01-raw-file-compression.Rmd` to add compressed versions of the raw data files and to compress the static figure for the manuscript. Also, knit the file to make sure the md version is up to date.

3. Manually run the code in `code/02-data-preparation.Rmd` to create the versions of the data to be used in the manuscript and submitted with the manuscript. Also, knit the file to make sure the md version is up to date.

@@

    # Create a vector with code and data files to be included for submission 
    data_files <-
      c(
        "../data/readme.txt",
        "../data/bullet-test.csv.zip",
        "../data/bullet-train.csv.zip",
        "../data/example-signatures.csv.zip"
      )

@@

7. Compile the file `paper.tex` to make sure it compiles correctly (especially references). (If using texShop, make sure to compile using LaTex, then bibTex, then LaTeX twice more.)

@@

10. Knit this document to make sure the md version is up to date.
